Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-18 overview.tex
added some cites

Distributed systems typically consist of two or more components that communicate \emph{asynchronously} by sending and receiving messages through a network layer. When a component receives a message, it responds by executing a predefined \emph{message handler}. This handler consists of a sequence of program statements that might update the internal state of the component, send a message to another component in the system, or even create an entirely new component.

@@

TODO: Quickly say how we found Cheng's bug?

\subsection{Distributed systems testing today}
\label{sec:overview:testing}

How cheng was testing his code before and how after -- high level, pretty picture

@@

Insert fancy \psharp picture

@@

mention dependency injection pattern?

>>>>

Distributed systems typically consist of two or more components that communicate \emph{asynchronously} by sending and receiving messages through a network layer~\cite{lamport1978time}. When a component receives a message, it responds by executing a predefined \emph{message handler}. This handler consists of a sequence of program statements that might update the internal state of the component, send a message to another component in the system, or even create an entirely new component.

@@

\PDComment{Quickly say how we found Cheng's bug?}

\subsection{Testing distributed systems today}
\label{sec:overview:testing}

Although a significant amount of research has been conducting during the past few decades on how to test distributed systems,

only a small amount of this research was successful enough to be picked up by industry.

\PDComment{How cheng was testing his code before and how after -- high level, pretty picture}

@@

\PDComment{Insert fancy \psharp picture}

@@

\PDComment{mention dependency injection pattern?}
